INTELLIGENT SYSTEMS

### 2021-04-14 papers/paper_7.tex
finish paper7

\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.8\linewidth]{images/paper7/crop result.png}
    \centering
    \caption{PSNR result of different methods on cropped real noisy images.}
    \label{fig:cropRes}
\end{figure}

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.7\linewidth]{images/paper7/crop result.png}
    \centering
    \caption{PSNR result of different methods on cropped real noisy images.}
    \label{fig:cropRes}
\end{figure}

\subsection{CONCLUSION}
Noise removal, as well as being carried out by the denoiser, is given by the 
learning made by the CNN network on the new input images which, through 
an iterative process, are gradually improved. This is possible only thanks to 
the estimates derived from the EM algorithm and how this can classify the 
various types of noise. Without this information, each input image would 
not get the proper correction, thus generating incorrect output images.
